---
title: "Text Mining Analysis"
author: "Anastasia Kunz"
date: "2/22/2021"
output:
  html_document:
    theme: flatly
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tidytext)
library(textdata)
library(pdftools)
library(ggwordcloud)
library(png)
library(here)
library(grid)
```

## The Odyssey - Robert Fagles Translation

Analysis of Homer's epic tale *The Odyssey*, translated by Robert Fagles.

*The Odyssey* tells the story of Odysseus's ten year voyage home to Ithaca after the Trojan War. It recounts the trials he faces, both natural and divine, that slow his journey home to his wife Penelope and son Telemachus. 

```{r}
odyssey_text <- pdf_text("Odyssey.pdf")

# Start tidy format

odyssey_tidy <- data.frame(odyssey_text) %>% 
  mutate(text_full = str_split(odyssey_text, pattern = "\\n")) %>% 
  unnest(text_full) %>% 
  mutate(text_full = str_squish(text_full))

#Make dataframe

odyssey_df <- odyssey_tidy %>% 
  slice(-(1:5)) %>% 
  mutate(book = case_when(
    str_detect(text_full, "Book") ~ text_full,
    TRUE ~ NA_character_
  )) %>% 
  fill(book) %>% 
  separate(col = book, into = c("bk", "no"), sep = " ") %>% 
  mutate(book = as.numeric(as.roman(no)))

# Word counts by book

odyssey_tokens <- odyssey_df %>% 
  unnest_tokens(word, text_full) %>% 
  select(-odyssey_text)



```

```{r, include=FALSE}
# take out stop words
odyssey_nonstop <- odyssey_tokens %>% 
  anti_join(stop_words)
```


## Top 100 Words in The Odyssey

Pictured below: Odysseus sailing along the sea of 100 most used words in *The Odyssey*

```{r}
# Count by book

odyssey_counts <- odyssey_nonstop %>% 
  count(word)
#create word cloud for whole book top 100 words

odyssey_top100 <- odyssey_counts %>% 
  arrange(-n) %>% 
  slice(1:100)

boat <- png::readPNG( "odyssey.png") #read and add png

ggplot(data = odyssey_top100, aes(label = word))+
  geom_text_wordcloud(aes(color = n, size = n), shape = "square")+
  scale_size_area(max_size = 6) +
  scale_color_gradientn(colors = c("royalblue2","cyan4", "turquoise2"))+
  theme_minimal()+
  annotation_custom(rasterGrob(boat, width = .1, height = .1),
                    0, 1.5,0, 1.7)

```



## Sentiment Analysis

Journey through the sentiment of *The Odyssey*, experiencing the ups and downs through time along the voyage home (by book).

```{r, include = FALSE}
# using afinn to track sentiment through "journey"
odyssey_afin <- odyssey_nonstop %>% 
  inner_join(get_sentiments("afinn"))

```

```{r}


afinn_count <- odyssey_afin %>% 
  group_by(book) %>% 
  summarize(mean_afinn = mean(value))

ggplot(data = afinn_count, aes(x = as.factor(book), y = mean_afinn))+
  geom_col(aes(fill = mean_afinn))+
  scale_fill_gradient2("Afinn Sentiment Value",low = "indianred", mid = "purple3", high = "navyblue", midpoint = 0,)+
  theme_minimal()+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  labs(
    x = "Book Number",
    y = "Average Afinn Value",
    title = "Average Sentiment Value Through Odyssey Journey"
  )

```







